% arara: xelatex
% arara: make: { task: "cv.png" }
\documentclass{simplecv}
\usepackage{lmodern}
\BetterSetup{
  textout = \jobname.cv.txt,
  textout-preamble = preamble.txt,
}
%\CensorInformation

\usepackage{additional-setup}
\usepackage{ragged2e}

\ContactInformation{
    name   = Mridula Natrajan,
    email  = mrna6782@colorado.edu,
    github = https://github.com/mridulanatrajan,
    phone  = 973\,342\,8054,
    street = 2754 Moorhead Avenue Apt 103,
    city   = Boulder,	,
    state  = Colorado,
    zip    = 80305,
}

\newif\ifmath
\newif\ifgithub
\newif\ifinterests

\IfCensoredTF{}{\IfFileExists{./contact-info.tex}{\input{contact-info}}{}}

\mathtrue
\githubtrue
\intereststrue
\begin{document}
\maketitle

\section{Education} 
\begin{education}
  {
      major = \textbf{Computer Science},
      degree = Master of Science,
      school = CU Boulder,
      school-link = http://www.colorado.edu/cs/,
      state = CO,
      city = Boulder,
      date = 2016 - \textit{expected} 2018,
  }

\begin{description}
     \item[Current Coursework]
       \course{Natural Language Processing},
       \course{Linear Programming}
      \item[Planned coursework]
        \course{Machine Learning},
        \course{Theory of Computation},
        \course{Advanced Robotics}
      \item[Datascience Team] Part of the Datascience team that works towards machine learning and natural language processing exercises.
\end{description}
\end{education}
\begin{education}
  {
      major = \textbf{Information Technology},
      degree = Bachelor of Technology,
      school = VIT University,
      school-link = http://www.vit.ac.in/,
      state = India,
      city = Vellore,
      date = 2010 - 2014,
  }
\begin{description}
    \item[Relevant Coursework]
      \course{Data structure and Algorithm},
      \course{Artificial Intelligence},
      \course{Linear Algebra},
      \course{Numerical Analysis}
    \item[Cisco Centre of Engineering Excellence] Selected to be a part of CCoEE. Researched on various networking protocols and implemented them on networking devices.
    \item[CGPA] 8.95/10
\end{description}
\end{education}
  \section{Work Experience}

\begin{position}
  {
      title   = \textbf{Technical Services Engineer},
      company = Cisco Systems,
      state= India,
      city= Bangalore,
      date    = July 2014- May 2016,
  }

  \begin{itemize}
      \item  Worked on application layer technologies such as ACE,WAVE and UCS-E. 
      \item  Troubleshot issues in live networks and restored them to production.
      \item  Led an initiative to teach the basics of CCNA to differently abled employees of Cisco
      \item  Worked as a part of the CSR team to help raise funds for underprivildged children suffering from cancer.
\end{itemize}
\end{position}
\vfill
\begin{position}
  {
      title   = \textbf{Technical Services Intern},
      company = Cisco Systems,
      city= Bangalore,
      date    = Jan 2014-July 2014,
  }

\begin{itemize}
    \item Worked in Technical Services Lab in order to build Network topologies and replicate issues in customer network
    \item shadowed engineers from various technical departments such as routing, switching, wireless and security.   
 \end{itemize}
\end{position}

\section{Technical Summary}
\begin{minipage}{\textwidth}
\begin{description}



 \item[Languages]
    Python,
    C,
    Java,
    \CPP,
    \TeX 
\item[Web  Designing]
    HTML,
    CSS,
    Javascript,
    PHP
  
\item[Software] 
    MATLAB,
    Wireshark,
    foma
     
\item [Operating  Systems \& Middleware]
     Linux (Ubuntu)
     
\item[Protocols]
    TCP/IP,
    HTTP
  
\item[Certifications]
	CCNA Routing  \& Switching,
	CCNP Routing \& Switching
      
\end{description}
\end{minipage}
\section{Projects}


\begin{position}
     {
      title   = \textbf{Traffic Disector},
      company = Cisco Systems,
      date = Jan 2014 - July 2014,
      }
      \begin{itemize}    
	      \item Created an application that discovers and displays a network topology.	      
        \item Contained features to display the interface and protocol wise statistics.
        \item Used Cisco's OnePK SDK for SDN in order to accomplish this.
        \item Primary Language used was C
	     \end{itemize}
 \end{position}
 \vfill                                                                      
 \begin{position}
   {
    title   = \textbf{Shortest Path Grid },
    company = VIT, 
    date    =  Jan 2013 - May 2014,
   }
	 \begin{itemize}
        \item  Deployed Dijkstra's Algorithm in a grid system of four computers.
        \item  Used Java language to implement the same.
    \end{itemize}
	\end{position}
\vfill
   \begin{position}
   {
    title   = \textbf{Cardoholic},
    company = VIT, 
    date    =  Jan 2013 - May 2013,
   }
	 \begin{itemize}
        \item  Created a website that allowed it's users to customize and design greeting cards.
        \item  Developed a customization page using Adobe Flash Professional CS5 and ActionScript3.
        \item  Devloped front-end using HTML, CSS and Flash and back-end using Javascript, PHP.
    \end{itemize}
	\end{position}

 
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% TeX-PDF-mode: t
%%% TeX-command-default: "arara"
%%% TeX-engine: xetex
%%% End:

%  LocalWords:  gpa adraig Jamieson Mathematica Powerpoint OneNote
%  LocalWords:  JSON cli YASCA Camtasia tri PDF PostgreSQL Visio CTAN
%  LocalWords:  Visio Redmine company-link title-link StackExchange
%  LocalWords:  StackMode ghkey vermiculus
